SpatialEpi

### 2016-08-20 README.Rmd
Updated README

```{r, message=FALSE, warning=FALSE, fig.height=8}
plotmap(cases/population, sp.obj, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

@@

```{r, cache=TRUE, fig.height=8}
plotmap(output$post_map$high_area, sp.obj)
```

>>>>

```{r, message=FALSE, warning=FALSE, fig.height=6.5}
plotmap(cases/population, sp.obj, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

@@

```{r, cache=TRUE, fig.height=6.5}
plotmap(output$post_map$high_area, sp.obj)
```
